\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\name{Umang}{Deval}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-10mm}
\begin{center}
\begin{tabular}{ c c c }
\faMobile\enspace \href{tel:+16476746408}{+1 (647) 674 6408}& \enspace\faEnvelope \enspace  \href{mailto:udeval@uoguelph.ca}{udeval@uoguelph.ca}& \enspace\faHome\enspace Guelph, Canada\\
\end{tabular}
\end{center}
\begin{center}
 \faLinkedin\enspace \href{https://www.linkedin.com/in/umang-deval-13b304241}{linkedin.com/in/umang-deval-13b304241}
 \faGithub\enspace \href{https://github.com/umangdeval}{github.com/umangdeval}   
\end{center}

\section{Technical Skills}

\begin{multicols}{3}

\subsection*{Programming Languages}
\begin{itemize}[label={\textbullet}, itemsep=0pt]
    \item Java
    \item C\#
    \item C
    \item Python
 
\end{itemize}

\subsection*{Web Technologies}
\begin{itemize}[label={\textbullet}, itemsep=0pt]
    \item HTML
    \item CSS
    \item Angular   
    \item React
    \item PHP
    \item JavaScript
    \item Spring
\end{itemize}

\subsection*{Other Skills}
\begin{itemize}[label={\textbullet}, itemsep=0pt]
    \item Git
    \item .Net
    \item Object-Oriented Programming
    \item Project Management
    \item Linux
    \item Windows
    \item MacOS
    \item Agile Methods
    \item Testing
\end{itemize}

\end{multicols}
\section{Personal Project}
\customcventry{2025}{{}}{SmartStudy – Personalized Study Planner (Under Development)}{}{}{
    \begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
        \item Currently developing a full-stack web application that helps students create adaptive study schedules and track progress.
        \item Building the frontend using React and the backend with Node.js and Express; utilizing MongoDB for data management.
        \item Integrating Google Calendar to enable automatic syncing of study sessions and reminders (in progress).
        \item Designed to include dynamic scheduling, gamified progress tracking, and a visual dashboard for enhanced learning engagement.
    \end{itemize}
}

\customcventry{2025}{{}}{QuickLearn – AI-Powered Microlearning Platform (GDSC Hackathon)}{}{}{
    \begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
        \item Co-developed a full-stack web application that generates personalized learning roadmaps using Google’s Vertex AI (Gemini).
        \item Built a responsive frontend in React and implemented the backend using Java with Spring Boot.
        \item Integrated AI APIs to dynamically generate step-by-step learning paths based on user-entered tech skills.
        \item Collaborated in a 4-member team; practiced version control with Git and presented the project at the GDSC 2025 Hackathon.
    \end{itemize}
}
\customcventry{2024}{{}}{Blackjack GUI}{}{}{
    \begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
        \item Developed a Graphical User Interface (GUI) for a Blackjack game using Java and JavaFX, implementing object-oriented programming principles.
        \item Incorporated game logic, user interaction, and visual elements to create an engaging and interactive user experience.
    \end{itemize}
}
\section{Education}
\customcventry{2023-Present}{{\color{blue}\href{https://www.uoguelph.ca/}{University of Guelph}}}{Bachelor of Computing, Computer Science (Co-op)}{Guelph, Ontario}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Made onto Dean's list for Fall 2023 
\item Completing a minor in Economics
\end{itemize}}}
\customcventry{2022-2023}{{\color{blue}\href{https://www.sheridancollege.ca/}{Sheridan College}}}{Diploma in Computer Programming}{Brampton, Ontario}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Graduated with 3.57 GPA
\end{itemize}}}

\section{Work Experience}
\customcventry{05/2025 ‐ 08/2025}{{\color{blue}\href{https://www.linkedin.com/company/ledgerai1/}{(Ledger Software – Singapore)}}}{Software Development Intern}{Remote}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Contributed to the development of a full-stack AI-powered POS system using React, JavaScript, Flask, and Django, improving efficiency and scalability for small businesses in the Singapore market.
\item Participated in agile sprints, conducted code reviews, and collaborated with a global development team, enhancing sprint velocity and feature delivery.
\item Designed and tested RESTful APIs and microservices; implemented Docker for application containerization and deployment across development environments.
\item Gained hands-on experience integrating AI features into web applications, enhancing system intelligence and user experience.
\end{itemize}}}

\customcventry{09/2023 ‐ 4/2025}{{\color{blue}\href{https://housing.uoguelph.ca}{(University Of Guelph Housing)}}}{Guest Registration and Door Staff,}{Guelph, Ontario}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Demonstrated effective communication skills and attention to detail by accurately maintaining client records and databases, ensuring proper access control. \item Collaborated with a cross-functional team to ensure seamless operations, exhibiting strong teamwork and adaptability in a dynamic environment.
\end{itemize}}}
\customcventry{Aug 2022 - Apr 2023}{{\color{blue}\href{https://www.walmart.ca}{(Walmart Canada)}}}{Retail Associate,}{Milton, Ontario}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
    \item Provided exceptional client service by recommending solutions and addressing product inquiries, leveraging strong communication and problem-solving skills.
    \item Exhibited a commitment to continuous learning and adaptability by actively receiving training on company policies and procedures.
\end{itemize}}}
\customcventry{08/2019 ‐ 12/2019}{{\color{blue}{(Anand Niketan)}}}{IT Head}{Ahmedabad, India}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Managed all audio-visual equipment and IT systems for school-wide events, ensuring reliable setup and technical performance.
\item Produced and edited custom event videos and soundtracks, enhancing presentation quality and audience engagement.
\item Collaborated with school administration and event staff to ensure seamless coordination of technical requirements across multiple functions.
\end{itemize}}}




\end{document}